Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-01 outputs/paper/paper.qmd
Added code to generate table of contents
Removed packages and code to plot spatial data

---
title: "Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election"
author: "Inessa De Angelis"
thanks: "Code and data from this analysis are available at: https://github.com/InessaDeAngelis/Toronto_Elections" 
date: "today"
date-format: "long" 
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: ref.bib
---

@@

## Load packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)
library(sf)
library(ggplot2)
library(ggspatial)
library(lubridate)

@@

### Results

@@

# code referenced from: https://sharlagelfand.github.io/opendatatoronto/articles/articles/spatial_data.html
cleaned_voting_locations |>
  c("address_full", "geometry")
ggplot() +
  geom_sf(data = address) +
  geom_sf(data = geometry) +
  theme_void()

@@

head (cleaned_voter_statistics, 5) |>
 select(ward, sub) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )

@@

```
### Discussion

### Conclusion

### References

>>>>

---
title: "Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election"
author: "Inessa De Angelis"
thanks: "Code and data from this analysis are available at: https://github.com/InessaDeAngelis/Toronto_Elections" 
date: "today"
date-format: "long" 
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: ref.bib
---

@@

## Load packages
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)
library(ggplot2)
library(lubridate)

@@

## Results

@@

#code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
cleaned_voter_statistics |>
  ggplot(aes(x = ward), "-", sub, fill = location_type) + 
  geom_bar() + #bar graph
  theme_minimal() + #neater theme
  theme(axis.text.x = element_text(angle=90, size = 6)) + #rotate x-axis & smaller font
  labs(
    title = "Number of Subdivisions Per Ward in Toronto",
    x = "Ward",
    y = "Number of Subdivisions",
    fill = "Type"
  )  #a

@@

head (cleaned_voter_statistics, 60) |>
 select(ward, sub) |>
  arrange (ward) |>
   kable(
    col.names = c("Ward", "Sub"),
  booktabs = TRUE
  )

@@

```
## Discussion

## Conclusion

## References
